---
title: "Adrian's"
output:
  html_notebook: default
---

Initializing Packages
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(broom)
library(readxl)
library(lubridate)
library(devtools) 
library(magrittr)
library(nlcor)
library(forcats)
```

Dataset 
```{r}
options(scipen = 999)
box_office <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 1)
title_performance <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 2)
twitter <- read.csv("data/Recruitment x Box Office x Q1 2019 - Twitter.csv", sep="\t", header=TRUE, fill = TRUE)
film_genre <- read.csv("data/genre_title.csv")
film_franchise <- read.csv("data/franchise_title.csv")

```

Data Cleaning
```{r}
twitter$post_date_time <- gsub("T.*", "", twitter$post_date_time) #remove details on time
twitter$post_date_time <- ymd(twitter$post_date_time)
twitter$title <- as.factor(twitter$title)
twitter$Year <- format(twitter$post_date_time , "%G") #creating a year column
twitter$Week <- format(twitter$post_date_time , "%V") #creating a week of the year column
twitter$Month <- format(twitter$post_date_time , "%B") #creating a month column
levels(twitter$title) <- gsub("beauty and the beast", "Beauty and the Beast", levels(twitter$title)) #title consistency
twitter$ID <- as.numeric(twitter$ID) #making column into numeric


box_office$Studio <- as.factor(box_office$Studio) #classifying studios into factors
box_office$Year <- as.factor(box_office$Year) #classifying years into factors
box_office$`Weekend Gross` <- str_remove_all(box_office$`Weekend Gross`, "[AU$,]") #removing obstructive strings
box_office$`Weekend Gross` <- as.numeric(box_office$`Weekend Gross`) #transforming column into numeric
box_office$`This Week's Rank` <- str_remove_all(box_office$`This Week's Rank`, "N-") #removing obstructive strings
box_office$`Last Week's Rank` <- str_remove_all(box_office$`Last Week's Rank`, "[N-]") #removing obstructive strings
box_office$`Last Week's Rank` <- sub(".0+$", "", as.character(box_office$`Last Week's Rank`)) #removing obstructive strings
box_office$`Weeks Into Release` <- sub(".0+$", "", as.character(box_office$`Weeks Into Release`)) #removing obstructive strings
box_office$Title <-  gsub("\\s*\\([^\\)]+\\)","",as.character(box_office$Title))
box_office$Title <- as.factor(box_office$Title) #classifying titles into factors
levels(box_office$Title) <- gsub("Dr. Seuss' The Grinch", "The Grinch", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Avengers: Infinity War", "Avengers Infinity War", levels(box_office$Title))#making titles consistency
levels(box_office$Title) <- gsub("Beauty and the Beast", "Beauty and the Beast", levels(box_office$Title))#making titles consistency
levels(box_office$Title) <- gsub("Jurassic World: Fallen Kingdom", "Jurassic World", levels(box_office$Title))#making titles consistency
levels(box_office$Title) <- gsub("Jurassic World: Fallen Kingdom", "Jurassic World", levels(box_office$Title))#making titles consistency
levels(box_office$Title) <- gsub("Occupation (2018)", "Occupation", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Night School", "Night School", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("The Predator", "Predator", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Sweet Country", "Sweet Country", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Sweet Country", "Sweet Country", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Dr. Seuss' The Grinch", "The Grinch", levels(box_office$Title)) #making titles consistency


title_performance$Title <- as.factor(title_performance$Title) #transforming title into factor
title_performance$Date <- gsub("(.*)–.*","\\1",title_performance$Date) #removing obstructive strings
title_performance$Date <- str_remove_all(title_performance$Date, "[.-]") #removing obstructive strings
title_performance$`Weekend Gross` <- str_remove_all(title_performance$`Weekend Gross`, "[.0]") #removing obstructive strings
title_performance$`Weekend Gross` <- as.numeric(title_performance$`Weekend Gross`)
title_performance$`Week # of release` <- as.numeric(title_performance$`Week # of release`) #transforming column into numeric
title_performance$`Gross-to-Date` <- as.numeric(title_performance$`Gross-to-Date`)
title_performance$new_date <- paste(title_performance$Year, title_performance$Date, sep="-") %>% ymd() %>% as.Date() #making it into date
title_performance$Week <- format(title_performance$new_date , "%V") #Week of the year
levels(title_performance$Title) <- gsub("Avengers: Infinty War", "Avengers Infinity War", levels(title_performance$Title)) #title consistency
levels(title_performance$Title) <- gsub("The Predator", "Predator", levels(title_performance$Title))
```

Creating a New Dataframe to understand twitter statistics + merging box office sales, weeks, etc. 
```{r}
twitter_stats <- twitter %>%
  select(Title = title, ID, Year, Week, Month) #Creating a new dataframe to work with Twitter Data
twitter_stats <- twitter_stats %>%
  group_by(Title) %>%
  mutate(cumulative_tweet_count = sum(ID))
twitter_stats <- twitter_stats %>%
  group_by(Title, Week) %>%
  mutate(weekly_tweet_count = sum(ID)) #weekly tweet count for film
twitter_stats <- unique(twitter_stats) #summarizing to show weekly features by selecting unique traits in dataset (which are the weekly differences)

twitter_stats_combined <- merge(twitter_stats, box_office, by.x=c("Title"), by.y=c("Title")) #combining twitter statistics with box office performance

twitter_stats_combined <- merge(twitter_stats_combined, film_genre, by.x=c("Title"), by.y=c("Title")) #combining twitter statistics with box office performance


twitter_stats_combined <- twitter_stats_combined %>% 
  group_by(Title) %>%
  mutate(cumulative_income = sum(`Weekend Gross`)) #including cumulative sum of box office performance

twitter_stats_combined <- twitter_stats_combined %>%
  distinct() #Showing only distinct information to remove duplicates

twitter_stats_combined <- twitter_stats_combined %>% 
  rename(Year = Year.x) %>%
  rename(Week = Week.x) %>% 
  rename(Weeks_into_release = `Weeks Into Release`) %>%
  rename(Last_week_rank = `Last Week's Rank`) %>%
  rename(Weekend_Gross = `Weekend Gross`) %>%
  select(!Year.y) %>%
  select(!Week.y)
```

## Visualising relationship between Number of Tweets and Film Performance
### Macro-perspective
```{r}
Macro <- twitter_stats_combined %>% 
  ggplot() +
  aes(x=cumulative_tweet_count, y=cumulative_income) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  geom_point() +
  labs(x="Cumulative Tweet Count", y="Cumulative Income", title = "Correlation between Cumulative Tweet Count and Cumulative Income by films") 

cor(twitter_stats_combined$cumulative_tweet_count, twitter_stats_combined$cumulative_income) #calculating correlation coefficient 
```

## A Weekly Perspective
```{r}
twitter_stats_combined %>% 
  ggplot() +
  aes(x=weekly_tweet_count, y=Weekend_Gross) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  geom_point() +
  labs(x="Number of Weekly Tweets", y="Weekend Gross", title = "Correlation between Weekly Tweet Count and Weekly Income of Film")

cor(twitter_stats_combined$weekly_tweet_count, twitter_stats_combined$Weekend_Gross) #calculating correlation coefficient 
```


## Faceting According to Studio
```{r}
Macro + facet_wrap(~Studio, ncol=3) + labs (subtitle = "Facet according to Studio") + theme(
  axis.text.x = element_text(angle = 45, hjust = 1)
  )



```


## Faceting According to Genre
```{r}
Macro + facet_wrap(~Genre, ncol=3) + labs (subtitle = "Facet according to Film Genre") + theme(
  axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Faceting According to Month
```{r}

twitter_stats_combined$Month <- factor(twitter_stats_combined$Month,levels = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December"))

# twitter_stats_combined$Month <- as.factor(twitter_stats_combined$Month)


levels(twitter_stats_combined$Month)

Macro + facet_wrap(.~Month, ncol=4) + labs (subtitle = "Facet according to Month") + theme(
  axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```

## Faceting According to Franchise
```{r}

twitter_stats_combined <- merge(twitter_stats_combined, film_franchise, by.x=c("Title"), by.y=c("Title")) #combining twitter statistics with box office performance

twitter_stats_combined$Franchise <- as.factor(twitter_stats_combined$Franchise)

Macro <- twitter_stats_combined %>% 
  ggplot() +
  aes(x=cumulative_tweet_count, y=cumulative_income) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  geom_point() +
  labs(x="Cumulative Tweet Count", y="Cumulative Income", title = "Correlation between Cumulative Tweet Count and Cumulative Income by films") 

Macro + facet_wrap(~Franchise, ncol=2) + labs (subtitle = "Facet according to Franchise") + theme(
  axis.text.x = element_text(angle = 45, hjust = 1)
  )

```

