---
title: "Adrian's"
output:
  html_notebook: default
---

Initializing Packages
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(broom)
library(highcharter)
library(readxl)
library(lubridate)
library(magrittr)
```

Dataset 
```{r}
options(scipen = 999)
box_office <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 1)
title_performance <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 2)
twitter <- read.csv("data/Recruitment x Box Office x Q1 2019 - Twitter.csv", sep="\t", header=TRUE, fill = TRUE)
```

Data Cleaning
```{r}
box_office$Title <- as.factor(box_office$Title) #classifying titles into factors
box_office$Studio <- as.factor(box_office$Studio) #classifying studios into factors
box_office$Year <- as.factor(box_office$Year) #classifying years into factors
box_office$`Weekend Gross` <- str_remove_all(box_office$`Weekend Gross`, "[AU$,]") #removing obstructive strings
box_office$`Weekend Gross` <- as.numeric(box_office$`Weekend Gross`) #transforming column into numeric
box_office$`This Week's Rank` <- str_remove_all(box_office$`This Week's Rank`, "N-") #removing obstructive strings
box_office$`Last Week's Rank` <- str_remove_all(box_office$`Last Week's Rank`, "[N-]") #removing obstructive strings
box_office$`Last Week's Rank` <- sub(".0+$", "", as.character(box_office$`Last Week's Rank`)) #removing obstructive strings
box_office$`Weeks Into Release` <- sub(".0+$", "", as.character(box_office$`Weeks Into Release`)) #removing obstructive strings
levels(box_office$Title) <- gsub("Dr. Seuss' The Grinch (2018)", "The Grinch", levels(box_office$Title)) #making titles consistent

title_performance$Title <- as.factor(title_performance$Title) #transforming title into factor
title_performance$Date <- gsub("(.*)–.*","\\1",title_performance$Date) #removing obstructive strings
title_performance$Date <- str_remove_all(title_performance$Date, "[.-]") #removing obstructive strings
title_performance$`Weekend Gross` <- str_remove_all(title_performance$`Weekend Gross`, "[.0]") #removing obstructive strings
title_performance$`Weekend Gross` <- as.numeric(title_performance$`Weekend Gross`)
title_performance$`Week # of release` <- as.numeric(title_performance$`Week # of release`) #transforming column into numeric
title_performance$`Gross-to-Date` <- as.numeric(title_performance$`Gross-to-Date`)
title_performance$new_date <- paste(title_performance$Year, title_performance$Date, sep="-") %>% ymd() %>% as.Date() #making it into date
title_performance$Week <- format(title_performance$new_date , "%V") #Week of the year
levels(title_performance$Title) <- gsub("Avengers: Infinty War", "Avengers Infinity War", levels(title_performance$Title)) #title consistency

twitter$post_date_time <- gsub("T.*", "", twitter$post_date_time) #remove details on time
twitter$post_date_time <- ymd(twitter$post_date_time)
twitter$title <- as.factor(twitter$title)
twitter$Year <- format(twitter$post_date_time , "%G") #creating a year column
twitter$Week <- format(twitter$post_date_time , "%V") #creating a week of the year column
levels(twitter$title) <- gsub("beauty and the beast", "Beauty and the Beast", levels(twitter$title)) #title consistency
twitter$ID <- as.numeric(twitter$ID) #making column into numeric
```

Creating a New Dataframe to understand twitter statistics + merging box office sales, weeks, etc. 
```{r}
twitter_stats <- twitter %>%
  select(Title = title, ID, Year, Week) #Creating a new dataframe to work with Twitter Data
twitter_stats <- twitter_stats %>%
  group_by(Title) %>%
  mutate(cumulative_tweet_count = sum(ID))
twitter_stats <- twitter_stats %>%
  group_by(Title, Week) %>%
  mutate(weekly_tweet_count = sum(ID)) #weekly tweet count for film
twitter_stats <- unique(twitter_stats) #summarizing to show weekly features by selecting unique traits in dataset (which are the weekly differences)

twitter_stats_combined <- merge(twitter_stats, box_office, by.x=c("Title", "Week"), by.y=c("Title", "Week")) #combining twitter statistics with box office performance
twitter_stats_combined <- twitter_stats_combined %>% 
  select(!Year.y) %>%
  select(!ID) %>%
  rename(Year = Year.x) #removing unnecessary columns and renaming columns
```

Looking for Trends: Visualising relationship between Weekend Gross and Number of Tweets
```{r}
twitter_stats_combined %>% 
  ggplot() +
  aes(y=`Weekend Gross`, x=weekly_tweet_count) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  geom_point() +
  labs(x="Weekly Tweet Counts", title = "Correlation between Weekend Gross and Weekly Tweet Counts") 
```

The visualisation suggests that there seem to be a positive linear correlation between film performance (represented by "Weekend Gross") and social buzz (represented by "Weekly Tweet Counts"). However, the error in estimate seems large as we can see that there is visible gap between data points and regression line. Moreover, there is a cluster that the line does not seem to interact with. 
