---
title: "Adrian's"
output:
  html_notebook: default
---

Initializing Packages
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
library(broom)
library(highcharter)
library(readxl)
library(lubridate)
library(magrittr)
```

Dataset 
```{r}
options(scipen = 999)
box_office <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 1)
title_performance <- read_excel("data/Recruitment x Box Office x Q1 2019.xlsx", sheet = 2)
twitter <- read.csv("data/Recruitment x Box Office x Q1 2019 - Twitter.csv", sep="\t", header=TRUE, fill = TRUE)
film_genre <- read.csv("data/genre_title.csv")
```

Data Cleaning
```{r}
box_office$Title <- as.factor(box_office$Title) #classifying titles into factors
box_office$Studio <- as.factor(box_office$Studio) #classifying studios into factors
box_office$Year <- as.factor(box_office$Year) #classifying years into factors
box_office$`Weekend Gross` <- str_remove_all(box_office$`Weekend Gross`, "[AU$,]") #removing obstructive strings
box_office$`Weekend Gross` <- as.numeric(box_office$`Weekend Gross`) #transforming column into numeric
box_office$`This Week's Rank` <- str_remove_all(box_office$`This Week's Rank`, "N-") #removing obstructive strings
box_office$`Last Week's Rank` <- str_remove_all(box_office$`Last Week's Rank`, "[N-]") #removing obstructive strings
box_office$`Last Week's Rank` <- sub(".0+$", "", as.character(box_office$`Last Week's Rank`)) #removing obstructive strings
box_office$`Weeks Into Release` <- sub(".0+$", "", as.character(box_office$`Weeks Into Release`)) #removing obstructive strings
levels(box_office$Title) <- gsub("Dr. Seuss' The Grinch (2018)", "The Grinch", levels(box_office$Title)) #making titles consistency
levels(box_office$Title) <- gsub("Avengers: Infinity War", "Avengers Infinity War", levels(box_office$Title))
levels(box_office$Title) <- gsub("Beauty and the Beast (2017)", "Beauty and the Beast", levels(box_office$Title))
levels(box_office$Title) <- gsub("Jurassic World: Fallen Kingdom", "Jurassic World", levels(box_office$Title))
levels(box_office$Title) <- gsub("Jurassic World: Fallen Kingdom", "Jurassic World", levels(box_office$Title))
levels(box_office$Title) <- gsub("Occupation (2018)", "Occupation", levels(box_office$Title))
levels(box_office$Title) <- gsub("Night School (2018)", "Night School", levels(box_office$Title))
levels(box_office$Title) <- gsub("The Predator (2018)", "Predator", levels(box_office$Title))
levels(box_office$Title) <- gsub("Sweet Country (2017)", "Sweet Country", levels(box_office$Title))
levels(box_office$Title) <- gsub("Sweet Country (2017)", "Sweet Country", levels(box_office$Title))
levels(box_office$Title) <- gsub("Dr. Seuss' The Grinch (2018)", "The Grinch", levels(box_office$Title))


title_performance$Title <- as.factor(title_performance$Title) #transforming title into factor
title_performance$Date <- gsub("(.*)–.*","\\1",title_performance$Date) #removing obstructive strings
title_performance$Date <- str_remove_all(title_performance$Date, "[.-]") #removing obstructive strings
title_performance$`Weekend Gross` <- str_remove_all(title_performance$`Weekend Gross`, "[.0]") #removing obstructive strings
title_performance$`Weekend Gross` <- as.numeric(title_performance$`Weekend Gross`)
title_performance$`Week # of release` <- as.numeric(title_performance$`Week # of release`) #transforming column into numeric
title_performance$`Gross-to-Date` <- as.numeric(title_performance$`Gross-to-Date`)
title_performance$new_date <- paste(title_performance$Year, title_performance$Date, sep="-") %>% ymd() %>% as.Date() #making it into date
title_performance$Week <- format(title_performance$new_date , "%V") #Week of the year
levels(title_performance$Title) <- gsub("Avengers: Infinty War", "Avengers Infinity War", levels(title_performance$Title)) #title consistency
levels(title_performance$Title) <- gsub("The Predator", "Predator", levels(title_performance$Title))

twitter$post_date_time <- gsub("T.*", "", twitter$post_date_time) #remove details on time
twitter$post_date_time <- ymd(twitter$post_date_time)
twitter$title <- as.factor(twitter$title)
twitter$Year <- format(twitter$post_date_time , "%G") #creating a year column
twitter$Week <- format(twitter$post_date_time , "%V") #creating a week of the year column
twitter$Month <- format(twitter$post_date_time , "%B") #creating a month column
levels(twitter$title) <- gsub("beauty and the beast", "Beauty and the Beast", levels(twitter$title)) #title consistency
twitter$ID <- as.numeric(twitter$ID) #making column into numeric
levels(twitter$title)
```

Creating a New Dataframe to understand twitter statistics + merging box office sales, weeks, etc. 
```{r}
twitter_stats <- twitter %>%
  select(Title = title, ID, Year, Week, Month) #Creating a new dataframe to work with Twitter Data
twitter_stats <- twitter_stats %>%
  group_by(Title) %>%
  mutate(cumulative_tweet_count = sum(ID))
twitter_stats <- twitter_stats %>%
  group_by(Title, Week) %>%
  mutate(weekly_tweet_count = sum(ID)) #weekly tweet count for film
twitter_stats <- unique(twitter_stats) #summarizing to show weekly features by selecting unique traits in dataset (which are the weekly differences)

twitter_stats_combined <- merge(twitter_stats, box_office, by.x=c("Title"), by.y=c("Title")) #combining twitter statistics with box office performance
twitter_stats_combined <- twitter_stats_combined %>% 
  group_by(Title) %>%
  mutate(cumulative_income = sum(`Weekend Gross`)) #including cumulative sum of box office performance

twitter_stats_combined <- merge(twitter_stats_combined, title_performance, by.x=c("Title"), by.y=c("Title"))

twitter_stats_combined <- twitter_stats_combined %>%
  select(Title, cumulative_tweet_count, cumulative_income) %>%
  distinct()




##
twitter_stats_combined <- twitter_stats_combined %>%
  select(Title, cumulative_tweet_count, cumulative_income) %>%
  distinct()

levels(twitter$title)

twitter_stats_combined$Title
```

# 1 Looking for Trends 
## 1.1 - Visualising relationship between Number of Tweets and Film Performance
```{r}
twitter_stats_combined %>% 
  ggplot() +
  aes(y=cumulative_tweet_count, x=cumulative_income) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  geom_point() +
  labs(x="Cumulative Tweet Counts", y="Cumulative Income", title = "Correlation between Cumulative Tweet Count and Cumulative Income by films")
```


## Regression Analysis of Cumulative Tweet Counts and Cumulative Income 
```{r}
cor(twitter_stats_combined$cumulative_tweet_count, twitter_stats_combined$cumulative_income) 
linearMod1 <- lm(cumulative_income ~ cumulative_tweet_count, data=twitter_stats_combined)
print(linearMod1)
summary(linearMod1) 
```


```{r}
twitter_stats_combined <- merge(twitter_stats_combined, film_genre, by.x=c("Title"), by.y=c("Title")) #adding genre into dataset

```

## 1.2 - Visualising relationship between Weekend Gross and Genre
```{r}

str(twitter_stats_combined)

twitter_stats_combined$Genre <- as.factor(twitter_stats_combined$Genre)
twitter_stats_combined %>%
  ggplot()
```


## 1.3 - Visualising relationship between Weekend Gross and Month
```{r}
twitter_stats_combined$Month <- factor(twitter_stats_combined$Month, levels = month.name) #sorting months into factor and arrange by chronological order


twitter_stats_combined %>%
  ggplot() +
  aes(y=`Weekend Gross`, x=Month) +
  geom_point()
```


